Program Optimisations via Hylomorphisms for Extraction of Executable Code

### 2025-07-07 paper/paper.tex
Link to code!

\subsection{Sorting Algorithms}\label{sec:sorting}
We now focus on divide-and-conquer sorting algorithms and demonstrate how to use
program calculation to apply a fusion optimisation. In the supplemental material
accompanying this paper, we formalise both mergesort and quicksort, but in this
section, we focus solely on quicksort. The recursive structure of quicksort is
given by the following functor
\begin{coqcode}
Inductive ITreeF A X := i_leaf | i_node (n : A) (l r : X)
\end{coqcode}
The idea is that a list is either empty or is split into a pivot which is
represented by node of type \coq{N} and the two sublists of type \coq{X}.

>>>>

\subsection{Sorting Algorithms}\label{sec:sorting}
We now focus on divide-and-conquer sorting algorithms and demonstrate how to use
program calculation to apply a fusion optimisation. In the supplemental material
accompanying this paper (\url{https://github.com/dcastrop/coq-hylomorphisms}), we formalise both mergesort and quicksort, but in this
section, we focus solely on quicksort. The recursive structure of quicksort is
given by the following functor
\begin{coqcode}
Inductive ITreeF A X := i_leaf | i_node (n : A) (l r : X)
\end{coqcode}
The idea is that a list is either empty or is split into a pivot which is
represented by node of type \coq{N} and the two sublists of type \coq{X}.
